A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2018-07-19 Manuscript/vaught_2017.tex
07/19/18

 \author{Fabrizio Arrigoni Battaia }
 \affiliation{Max-Planck-Institut fur Astronomie, Konigstuhl 17, D- 69117 Heidelberg, Germany}

@@

The mass and energy of galactic winds remain poorly constrained via traditional absorption line studies. One way to better constrain these parameters is to measure the spatial extent of the outflow in emission. We perform a VLT/FORS2 narrowband imaging of 5 star-forming galaxies at redshift $z=0.67-0.69$ in the GOODS-S field as part of an effort to spatially resolve and constrain the radial extent of large-scale outflows traced by \ion{Mg}{2} emission. These observations probe extended \ion{Mg}{2} emission down to unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).  We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, thus placing strong upper limits on the strength of \ion{Mg}{2} emission at projected distances $R_{\perp} = 8-21$ kpc from the sample galaxies. Our observations allow us to create the first ever spatially-resolved map of \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks. Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to model \ion{Mg}{2} emission for isotropic and anisotropic dust-free winds. We find that anisotropic winds reduce the strength of estimated missing \ion{Mg}{2} emission below our 5$\sigma$ limit.

@@

An accurate picture of what types of galaxies host outflows comes from numerous absorption line studies of galaxies (\citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}). Outflows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systematic velocity. Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g. \citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}). Even though these probes can constrain: the radial velocity, column density and covering fraction of the flow, this method is weak in constraining the overall radial extent and provides no information on the morphology of the outflow.

One way of developing these constraints is to trace the extent of winds in emission. This has been demonstrated using rest-frame optical transitions (i.e H$\alpha$, [\ion{O}{3}], etc) as tracers for winds around nearby starbursts (\citethnop{Matsubayashi2009}; \citethnop{Veilleux2009}; \citethnop{Tripp2011}) as these transitions can trace the warm shock heated phase of the gas. 
A novel, alternative transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet (UV)
(Weiner et al. 2009; Kornei et al. 2013)\nocite{Weiner2009, Kornei2013}. While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011}  recently observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.  This emission was the first detection of an outflow beyond the spatial extent of the galaxy continuum in the distant universe, with a minimum spatial extent  $>$ 7 kpc.

One proposed production mechanism for the galaxy's observed \ion{Mg}{2} line profile is photon scattering. In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions, $\lambda_{2796}$ and $\lambda_{2803}$. Once these transitions are excited, they may only decay back to the ground state and if the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons. Because the photons are absorbed in the rest frame of the gas, the absorption will be blueshifted relative to the galaxy's systematic velocity. The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind. Because the photons are redshifted, the photons will be able to travel freely towards the observer through the wind to produce emission at and redward of the systematic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}). Since the first detection of \ion{Mg}{2} emission by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
at $z=0.9392$.   \ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with Keck/DEIMOS and VLT/MUSE  (\citethnop{Erb2012} and Feltre et. al (2018)). These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles.  Detections of \ion{Mg}{2} in emission were found to be associated with galaxies of lower stellar mass and bluer spectral slopes.

@@

In Section \ref{sec:obs_red} we describe our sample of GOOD-S galaxies, supplemental Keck/LRIS spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration. We go into detail in our method of continuum subtraction in Section \ref{sec.cont_sub}. The analysis of these data is presented in Section \ref{sec:analysis}, 
including our methods for calculating surface brightness profiles and detection limits for each galaxy, as well as maps of \ion{Mg}{2} equivalent widths.
%in detail we discuss the production surface bright profiles and limits for each galaxy, as well as the production of narrowband %measured equivalent widths. 
Section \ref{sec:results} presents results from our narrowband imaging analysis. We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made by radiative transfer models in Section \ref{sec:discussion}. We conclude this paper in Section \ref{sec:conclusion}.
We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$.

\section{Observations and Data Reduction}\label{sec:obs_red}
\subsection{Sample Selection}
Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging (Rubin et al. 2014)\nocite{Rubin_2014}.  In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}) and the AEGIS survey field (the Extended Groth Strip; Davis et al. 2007)\nocite{Davis2007}.  In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 < z < 0.68$.  This peak is in fact the global maximum of the distribution, as all other bins of width $\Delta z = 0.02$ have at most four galaxies.  Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 4675$ and 4722 \AA\ which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.  We selected our final sample of five of these galaxies at $0.66 < z < 0.68$ to be close on the sky such that they could be imaged in a single $7' \times 7' $ FORS2 pointing.  
We show color {\it HST}/ACS images of these objects in Figure~\ref{fig:hstims}.

The absorption line modeling presented in (Rubin et al. 2014)\nocite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths (EW) $\sim 2-3$ \AA.  Modeling of the galaxy broad-band spectral energy distributions obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014}, are listed in Table \ref{tab:prop}.

@@

FORS2 has a native pixel scale of $0.125''$ pixel$^{-1}$ and a field of view of $7'\times7'$.  The data were taken with 
the CCD binned $2\times2$, yielding a pixel scale of $0.25''$ pixel$^{-1}$.
Images of three pointings offset by $0.25\arcmin$ East/West were obtained, with individual exposure times of $\approx$ 1000 sec.  A total of 38  exposures were taken in each filter. 
Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A). The seeing (see Figure \ref{fig.seeing}) ranged from $0.5\arcsec$ to $2.5\arcsec$. Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.

\begin{figure*}[!ht]
\centering
\includegraphics[scale=.73]{../Figures/fors2_color_imstamps.pdf}
\caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}). Each image is 5'' $\times$ 5''.\label{fig:hstims}}
\end{figure*}

@@

\begin{figure}[h]
\centering
\includegraphics[scale=.55]{../Figures/avg_seeing_HEII.pdf}
\includegraphics[scale=.55]{../Figures/avg_seeing_HEII3000.pdf}
\caption{  Distribution of seeing conditions for individual exposures comprising our dataset.
\textbf{Top}: Seeing distribution for the 38 HeII+47 images. The median seeing in this filter is $1.03\arcsec$.
\textbf{Bottom}: Same distribution for the 38 HeII/3000+48 images. The median seeing is $1.08\arcsec$. 
The seeing conditions were calculated by ESO and were provided in the header of each science image.
\label{fig.seeing}}
\end{figure}

@@

@@

\begin{table*}[t]
\centering
\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) include both components of the \ion{Mg}{2} doublet and were %calculated with Eq. \ref{eq:specEW} and 
determined from analysis of 
the supplemental Keck/LRIS spectra.}
\begin{tabular}{lllllll} \hline \hline
Object & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) \smallskip      \\ \hline 
J033225.26-274524.0      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$\\ 
%274524.0     & &  &  &         \\
J033231.36-274725.0       & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$\\
%274725.0      & &  &   &        \\
J033230.03-274347.3       & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$\\
%274347.3      & &  &   &        \\
J033229.64-274242.6      & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$\\
%274242.6     & &  &     &      \\
J033230.57-274518.2      & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ \\
%274518.2      & &  &  &         \\ 
\hline 
\end{tabular}
\label{tab:prop}
\end{table*}

\subsection{Absolute Flux Calibration}
We acquired observations of the standard star GD50 from archival ESO calibration imaging at 4 independent epochs. Performing aperture photometry at each epoch and airmass, we calculated the atmospheric extinction coefficients ($k$) to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter. We perform absolute flux calibration using the methods of Jacoby et al. (1990). We first convolve the spectral energy distribution of the standard star, $F(\lambda)$ in ergs sec$^{-1}$ \AA$^{-1}$ cm$^{-2}$, with that of the known transmission curve of the filter, $T_{i}(\lambda)$. This yields $F_i$, the total observable flux in each bandpass filter $i$ with units of ergs sec$^{-1}$ cm$^{-2}$:
\begin{equation*}
F_{i}=\int F(\lambda)T_{i}(\lambda)d\lambda.
\end{equation*}
It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. However, our filter transmission curves are sampled at $5$\ \AA\ intervals which is the same sampling as the spectral energy distribution of the standard star obtained from the ESO archives (WILL CHECK CALSPEC). Therefore we calculate the integral numerically.
The system sensitivity, including the defects of the telescope optics and detector response is then given by
\begin{equation*}
S_{i}=\dfrac{F_{i}}{C10^{k_{i}A}},
\end{equation*}\\
where $k_i$ is the extinction in magnitudes per airmass, A is the airmass for each individual exposure, C is the measured count rate of the standard star and $S_i$ is in units of ergs counts$^{-1}$ cm$^{-2}$. Before image co-addition, each science image is corrected for atmospheric extinction by multiplying each frame by $10^{k_{i}A}$. Next, the image is divided by the exposure time, effectively putting the image in units of counts per sec. After co-addition, the images are then multiplied by the appropriate sensitivity factor $S_{i}$. This puts the final images in the appropriate flux units, ergs sec $^{-1}$ cm$^{-2}$.

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.61]{../Figures/HEII_final.png}
\includegraphics[scale=.61]{../Figures/HEII3000_final.png}
\caption{Top: Stacked HeII+47 image of the galaxy sample. Bottom: Stacked HeII3000+48 image of the same pointing. The exposure time of each image is $\approx 10$ hours. Each image has a FOV of $7' \times 7'$ which fortuitously contains the full sample of galaxies (indicated by the blue circles). East is up and North is right.
\label{fig:stacked_image}}
\end{figure*}

\section{Image Subtraction}\label{sec.cont_sub}
We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
To reach both of these goals, we must perform accurate subtraction of the continuum flux of each object from the filter covering the targeted line emission. For four of the five objects in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame.

@@

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.7]{../Figures/stamps.pdf}
\caption{ $10'' \times 10''$ images of each galaxy in our sample. Top row: Continuum surface brightness in ergs/s/cm$^2$/sq.arcsec measured in the HeII/3000+48 filter. Bottom row: Continuum-subtracted \ion{Mg}{2} surface brightness.  Absorption can be seen in 4 of 5 galaxies. The red contours represent the outline of the 1$\sigma$ surface brightness limit in the HeII/3000+48 image, defined in Sec. \ref{sec.sb}. The colorbar shows the scaling used for the \ion{Mg}{2} images.}
\label{fig:stamp_images}
\end{figure*}

@@

\begin{figure*}
\centering
\gridline{\fig{../Figures/J033225_26.pdf}{0.5\textwidth}{(a)}
          \fig{../Figures/J033231_36.pdf}{0.5\textwidth}{(b)}}
\gridline{\fig{../Figures/J033230_03.pdf}{0.5\textwidth}{(c)}
          \fig{../Figures/J033230_64.pdf}{0.5\textwidth}{(d)}}
           \fig{../Figures/J033230_57.pdf}{0.5\textwidth}{(e)}
\caption{SB profiles for our sample galaxies. (Top panel) Continuum SB profile (black) measured for each galaxy. The green points show the Mg II + continuum SB measured for the galaxy in the pre-continuum subtracted image. The blue points show the Mg II line SB measured for the galaxy in the continuum subtracted line emission image.  The profile exhibits SB decrements from \ion{Mg}{2} absorption. Photometry was performed in circular annuli. (Bottom panel) The vertical hashes in the bottom show the inner and outer radius of each annulus in kpc. Distance from the center of the galaxy (x-axis) is computed using the average value of the inner and outer radii of each annulus.}
\label{fig:sb_profiles}
\end{figure*}

@@

Using the above equation along with the continuum and continuum-subtracted images, we produce images of the observed-frame EW$_{\rm{MgII}}$. The observed-frame  EW$_{\rm{MgII}}$ images are displayed in Figures \ref{fig:ew11}, \ref{fig:ew22}, \ref{fig:ew33}, \ref{fig:ew44}, \ref{fig:ew55},[\textbf{WILL CONSOLIDATE THESE FIGURES}] and show only the EWs within the 1$\sigma$ SB$_1$ contours of the corresponding \ion{Mg}{2} images (prior to continuum subtraction).

@@

%A fourth galaxy that needs additional phenomena like dust to reduce the SB of emission and be consistent with our observations.

>>>>

 \author{Fabrizio Arrigoni Battaia }
 \affiliation{European Southern Observatory, Karl-Schwarzschild-Str. 2, D-85748 Garching bei M\"unchen, Germany}

@@

The mass and energy of galactic winds remain poorly constrained via traditional absorption line studies. One way to better constrain these parameters is to measure the spatial extent of the outflow in emission. We perform a VLT/FORS2 narrowband imaging of 5 star-forming galaxies at redshift $z=0.67-0.69$ in the GOODS-S field as part of an effort to spatially resolve and constrain the radial extent of large-scale outflows traced by \ion{Mg}{2} emission. These observations probe extended \ion{Mg}{2} emission down to unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).  We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, thus placing strong upper limits on the strength of \ion{Mg}{2} emission at projected distances $R_{\perp} = 13-24$ kpc from the sample galaxies. Our observations allow us to create the first ever spatially-resolved map of \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks. Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to model \ion{Mg}{2} emission for isotropic and anisotropic dust-free winds. We find that anisotropic winds reduce the strength of estimated missing \ion{Mg}{2} emission below our 5$\sigma$ limit.

@@

An accurate picture of what types of galaxies host outflows comes from numerous absorption line studies of galaxies (\citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}). Outflows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systematic velocity.
 %Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g. \citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
Even though these probes can constrain: the radial velocity, column density and covering fraction of the flow, 
this method is weak in constraining the overall radial extent and provides no information on the morphology of the outflow.

One way of constraining the radial extent and morphology of the outflow is to trace winds in emission. This has been demonstrated using rest-frame optical transitions (i.e H$\alpha$, [\ion{O}{3}], etc) as tracers for winds around nearby starbursts (\citethnop{Matsubayashi2009}; \citethnop{Veilleux2009}; \citethnop{Tripp2011}) as these transitions can trace the warm shock heated phase of the gas. 
A novel, alternative transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet (UV)
(Weiner et al. 2009; Kornei et al. 2013)\nocite{Weiner2009, Kornei2013}. While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011} observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.  This emission was the first detection of an outflow beyond the spatial extent of the galaxy continuum in the distant universe, with a minimum spatial extent  $>$ 7 kpc.

One proposed production mechanism for the galaxy's observed \ion{Mg}{2} line profile is photon scattering. In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions, $\lambda_{2796}$ and $\lambda_{2803}$. Once these transitions are excited, they may only decay back to the ground state and if the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons. Because the photons are absorbed in the rest frame of the gas, the absorption will be blueshifted relative to the galaxy's systematic velocity. The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind. Because the photons are redshifted, the photons will be able to travel freely towards the observer through the wind to produce emission at and redward of the systematic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}). Since the first detection of \ion{Mg}{2} emission by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
at $z=0.9392$.   \ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with Keck/DEIMOS and VLT/MUSE  (\citethnop{Erb2012}, \citethnop{Feltre2018}). These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles.  Detections of \ion{Mg}{2} in emission were found to be associated with galaxies of lower stellar mass and bluer spectral slopes.

@@

In Section \ref{sec:obs_red} we describe our sample of GOOD-S galaxies, supplemental Keck/LRIS spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration. We go into detail in our method of continuum subtraction in Section \ref{sec.cont_sub}. The analysis of these data is presented in Section \ref{sec:analysis}, 
including our methods for calculating surface brightness profiles and detection limits for each galaxy, as well as maps of \ion{Mg}{2} equivalent widths.
%in detail we discuss the production surface bright profiles and limits for each galaxy, as well as the production of narrowband %measured equivalent widths. 
Section \ref{sec:results} presents results from our narrowband imaging analysis. We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made by radiative transfer models in Section \ref{sec:discussion}. We conclude this paper in Section \ref{sec:conclusion}.
We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$. In this cosmology, 1\arcsec is $\approx 7\ \rm kpc$ at $z \sim 0.7$.

\section{Observations and Data Reduction}\label{sec:obs_red}
\subsection{Sample Selection}
Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging \citep{Rubin_2014}.  In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}) and the AEGIS survey field (the Extended Groth Strip; Davis et al. 2007)\nocite{Davis2007}.  In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 < z < 0.68$.  This peak is in fact the global maximum of the distribution, as all other bins of width $\Delta z = 0.02$ have at most four galaxies.  Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 4675$ and 4722 \AA\ which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.  We selected our final sample of five of these galaxies at $0.66 < z < 0.68$ to be close on the sky such that they could be imaged in a single $7' \times 7' $ FORS2 pointing.  
We show color {\it HST}/ACS images of these objects in Figure~\ref{fig:hstims}.

The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths (EW) $\sim 2-3$ \AA.  Modeling of the galaxy broad-band spectral energy distributions obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. The properties and nomenclature of the sample, as well as precise target coordinates taken from \cite{Rubin_2014} ) are listed in Table \ref{tab:prop}.

@@

FORS2 has a native pixel scale of $0.125''$ pixel$^{-1}$ and a field of view of $7'\times7'$.  The data were taken with 
the CCD binned $2\times2$, yielding a pixel scale of $0.25''$ pixel$^{-1}$.
Images of three pointings offset by $0.25\arcmin$ East/West were obtained, with individual exposure times of $\approx$ 1000 sec.  A total of 38  exposures were taken in each filter. 
Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A). The seeing, which ranged from $0.5\arcsec$ to $2.5\arcsec$, are given in the image header and are derived from DIMM seeing measurements. These DIMM values are calculated from zenith observations of bright stars at 0.5 microns, which are then reduced to the zenith angles and wavelengths of the science observation. Additionally, a first order correction is then applied for appropriate for a 8m telescope is applied (see Figure \ref{fig.seeing})  Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.

\begin{figure*}[!ht]
\centering
\includegraphics[scale=.73]{../Figures/fors2_color_imstamps.pdf}
\caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}). Each image is 5'' $\times$ 5'' ( or about $ 40 \rm \ kpc \times 40 \rm \ kpc $) .\label{fig:hstims}}
\end{figure*}

@@

\begin{figure}[h]
\centering
\includegraphics[scale=.55]{../Figures/avg_seeing_HEII.pdf}
\includegraphics[scale=.55]{../Figures/avg_seeing_HEII3000.pdf}
\caption{\textbf{Top}: Distribution of seeings for the 38 HeII+47 images.
\textbf{Bottom}: Same HeII/3000+48 images. The median seeing conditions for the images in both filters is $\sim 0.8\arcsec$. 
The seeing conditions were calculated from DIMM measurements which are provided by ESO in the header of each science image.
\label{fig.seeing}}
\end{figure}

@@

\begin{table*}[t]
\centering
\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) include both components of the \ion{Mg}{2} doublet and were 
determined from analysis of the supplemental Keck/LRIS spectra.}
\begin{tabular}{llllllll} \hline \hline
Object\footnote{ Name in parenthesis to be used as shorthand for the objects throughout the remainder of the paper } & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) & $\tau_V$\footnote{ 97.5th percentile of the $\tau_V$ distribution}\smallskip      \\ \hline 
J033225.26-274524.0 (J.26)      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$ & 4.812\\

J033231.36-274725.0 (J.36)      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$ & 3.427\\

J033230.03-274347.3  (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$ & 2.867 \\

J033229.64-274242.6  (J.64)    & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$ & 5.042\\

J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ &4.022 \\

\hline 
\end{tabular}
\label{tab:prop}
\end{table*}

@@

\subsection{Absolute Flux Calibration}
We acquired observations of the standard star GD50 from archival ESO calibration imaging at 4 independent epochs. Performing aperture photometry at each epoch and airmass, we calculated the atmospheric extinction coefficients ($k$) to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter. We perform absolute flux calibration using the methods of Jacoby et al. (1990). We first convolve the spectral energy distribution of the standard star, $F(\lambda)$ in ergs sec$^{-1}$ \AA$^{-1}$ cm$^{-2}$, with that of the known transmission curve of the filter, $T_{i}(\lambda)$. This yields $F_i$, the total observable flux in each bandpass filter $i$ with units of ergs sec$^{-1}$ cm$^{-2}$:
\begin{equation*}
F_{i}=\int F(\lambda)T_{i}(\lambda)d\lambda.
\end{equation*}
It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. 
%However, our filter transmission curves are sampled at $5$\ \AA\ intervals which is the same sampling as the spectral energy distribution of the standard star obtained from the ESO archives (WILL CHECK CALSPEC). 
However, we calculate the integral numerically.
The system sensitivity, including the defects of the telescope optics and detector response is then given by
\begin{equation*}
S_{i}=\dfrac{F_{i}}{C10^{k_{i}A}},
\end{equation*}\\
where $k_i$ is the extinction in magnitudes per airmass, A is the airmass for each individual exposure, C is the measured count rate of the standard star and $S_i$ is in units of ergs counts$^{-1}$ cm$^{-2}$. Before image co-addition, each science image is corrected for atmospheric extinction by multiplying each frame by $10^{k_{i}A}$. Next, the image is divided by the exposure time, effectively putting the image in units of counts per sec. After co-addition, the images are then multiplied by the appropriate sensitivity factor $S_{i}$. This puts the final images in the appropriate flux units, ergs sec $^{-1}$ cm$^{-2}$.

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.61]{../Figures/HEII_final.png}
\includegraphics[scale=.61]{../Figures/HEII3000_final.png}
\caption{Top: Stacked HeII+47 image of the galaxy sample. Bottom: Stacked HeII3000+48 image of the same pointing. The exposure time of each image is $\approx 10$ hours. Each image shows half of the total FOV of $7' \times 7'$ which contains the full sample of galaxies (indicated by the white arrows). East is up and North is right.
\label{fig:stacked_image}}
\end{figure*}

\section{Image Subtraction}\label{sec.cont_sub}
We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
To reach both of these goals, we must perform accurate subtraction of the continuum flux of each object from the filter covering the targeted line emission. For four of the five galaxies in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame. The galaxy excluded from our analysis is instead used as a check on the quality of our continuum subtraction for reasons detailed in Section \ref{subsubsec:SBprofiles}.

@@

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.7]{../Figures/stamps.pdf}
\caption{ $10'' \times 10''$ (or about $70 \rm \ kpc \times 70 \rm \ kpc $) images of each galaxy in our sample. Top row: Continuum surface brightness in ergs s$^{-1}$ cm$^{-2}$ arcsec$^{-2}$ measured in the HeII/3000+48 filter. Bottom row: Continuum-subtracted \ion{Mg}{2} surface brightness.  Absorption can be seen in 4 of 5 galaxies. The red contours represent the outline of the 1$\sigma$ surface brightness limit in the HeII+47 image, defined in Sec. \ref{sec.sb}. The colorbar shows the scaling used for the \ion{Mg}{2} images.}
\label{fig:stamp_images}
\end{figure*}

@@

\begin{figure*}
\centering
\gridline{\fig{../Figures/J_26.pdf}{0.5\textwidth}{(a)}
          \fig{../Figures/J_36.pdf}{0.5\textwidth}{(b)}}
\gridline{\fig{../Figures/J_03.pdf}{0.5\textwidth}{(c)}
          \fig{../Figures/J_64.pdf}{0.5\textwidth}{(d)}}
           \fig{../Figures/J_57.pdf}{0.5\textwidth}{(e)}
\caption{SB profiles for our sample galaxies. (Top panel) Continuum SB profile (black) measured for each galaxy. The green points show the Mg II + continuum SB measured for the galaxy in the pre-continuum subtracted image. The blue points show the Mg II line SB measured for the galaxy in the continuum subtracted line emission image.  The profile exhibits SB decrements from \ion{Mg}{2} absorption. Photometry was performed in circular annuli. (Bottom panel) The vertical hashes in the bottom show the inner and outer radius of each annulus in kpc. Distance from the center of the galaxy (x-axis) is computed using the average value of the inner and outer radii of each annulus.}
\label{fig:sb_profiles}
\end{figure*}

@@

Using the above equation along with the continuum and continuum-subtracted images, we produce images of the observed-frame EW$_{\rm{MgII}}$. The observed-frame EW$_{\rm{MgII}}$ images are displayed for each galaxy in Figure \ref{fig:ews} and show only the EWs within the 1$\sigma$ SB$_1$ contours of the corresponding \ion{Mg}{2} images (prior to continuum subtraction).

@@

Based on the radial extent and strength of our measured \ion{Mg}{2} absorption, the \ion{Mg}{2} is optically thick. Deeper images in \ion{Mg}{2} are required to observe any extended emission beyond the depth of our images.  Although our detection limits suggest that the winds in our sample are not isotropic and dust-free, questions linger regarding the relative roles wind anisotropy, dust content, and extent play in reducing scattered emission.
